---
title: "Rotating image, crop, and read Cyrillic"
output: html_notebook
---
A sample script for rotating, and cropping newspaper images for extracting text.  Note that for multi-column texts, the best solution appears to be to crop each column in succession.

File 1 of 421 complete(!)

```{r}
library(tidyverse)
library(stringr)
library(magick)
library(tesseract)
if(is.na(match("rus", tesseract_info()$available)))
  tesseract_download("rus")
russian <- tesseract("rus")
```


```{r}


filelist <- list.files("./Scans/Processed images", full.names = TRUE)

###Extract metadata from filename

name.date <- str_sub(filelist[1], 43, -10)  #This should work for almost all filenames
article.title <- "Bear service to the president"            #Title can be entered manually, or cropped and run through OCR

###Read and edit image

image1 <- image_read(filelist[1])
image_browse(image1)

image_bearb1 <- image_rotate(image1, .5)
image_browse(image_bearb1)#If this particular image needed rotating

image_bearb2 <- image_crop(image_bearb1, geometry_area(width= 490, height= 952, x_off = 1809, y_off = 2235)) #This syntax is quite unclear, but it works like this
               #The first two numbers are the x and y cooridinates of the top left pixel of the cropped area
               #This is given in the window bar of the program Irfan Viewer
               #The other two numbers give the x length, y-length of the cropped area

image_browse(image_bearb2)
```

Now the OCR using `tesseract`, update number after 'text' to indicate which column is being scanned.

```{r}
text4 <- ocr(image_bearb2, engine = russian)
text4

text4 <- str_replace_all(text4, "[-\n]", "")
text4
```

Combine text from columns together if necessary

```{r}
text.complete <- paste(text1, text2, text3, text4)
#text.complete <- str_replace_all(text.complete, "[[.]]", ". ")  #If spaces after periods not showing up.
```
Sometimes spaces are not appearing after periods, so the `str_replac_all` call is used to add a space after all periods. The `[[.]] is used to call out the punctuation mark '.', which otherwise has a use in the code (i.e. it selects all).

Now it's necessary to save the text in a csv, along with metadata giving the newspaper name and date and article title. To save in csv, I transliterate the Cyrillic into Latin using `stringi`.

```{r}
data.text <- as_tibble(read.csv("text-dataframe.csv"))
data.text$text %<>% as.character

text.container <- tibble(text=NA, article.name=NA, newspaper.name.date=NA)

latin.text <- stri_trans_general(text.complete, "cyrillic-latin")

text.container$text[1] <- latin.text
text.container$newspaper.name.date[1] <- name.date
text.container$article.name <- article.title

data.text <- rbind(data.text, text.container)


write.csv(data.text, "text-dataframe.csv", row.names = FALSE)



```

Note that when analysing the data, it will be necessary to transliterate back into Cyrillic, using `stri_trans_general(text, "latin-cyrillic")`



